Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
\label{sec:governing_equations}
The governing equations are a system for the position and orientation of
a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
equations for the mobility problem giving the hydrodynamic interactions
for the particle suspension. The hydrophobic forces come from solving a
screened Laplace equation. Particle collisions are avoided through a
near-field, pair potential.

@@

Under a Taylor-Green flow, the amphiphilic JPs are the most interesting,
exhibiting different vesicle shapes depending on the ratio of the size
of the TG flow to the vesicle size. These results show that the shape of
the vesicle, whether square or polygonal, can be controlled by adjusting
the size of the cell in the TG flow. On the other hand, the assembly of
multilamellar JPs and the striated JPs behave more like a rigid body
with connected subdomains, and the number of subdomains increases with
increasing strength of the TG flow. Overall, the multilamellar (Type II)
JP assembly behaves as a shear-thinning fluid, while the striated (Type
III) JP assembly possesses a yield stress.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
\label{sec:governing_equations}
The governing equations are a system of partial differential equations for the position and orientation of
a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
equations for the mobility problem giving the hydrodynamic interactions
for the particle suspension. The hydrophobic forces come from solving a
screened Laplace equation. Particle collisions are avoided through a
near-field, pair potential.

@@

Under a Taylor-Green flow, the amphiphilic JPs are the most interesting,
exhibiting different vesicle shapes depending on the ratio of the size
of the TG flow to the vesicle size. These results show that the shape of
the vesicle, whether square or polygonal, can be controlled by adjusting
the size of the cell in the TG flow. In addition the permeability of the JP bilayer
varies non-monotonically with the TG cell size.
%
On the other hand, the assembly of
multilamellar JPs and the striated JPs behave more like a rigid body
with connected subdomains, and the number of subdomains increases with
increasing strength of the TG flow. Overall, the multilamellar (Type II)
JP assembly behaves as a shear-thinning fluid, while the striated (Type
III) JP assembly possesses a yield stress.
